---
title: "Color exercise"
author: "Schwab"
format: html
---

Let's play around with some colors.  

```{r message=FALSE}
library(openintro)
library(tidyverse)
library(RColorBrewer)
library(ggthemes)
```



Let's play with themes. Add theme_bw(), theme_economist(), theme_dark(), theme_classic()

```{r}
president |>
  ggplot(aes(x=start, y =end, color = party) )+
  geom_point()+
  theme_bw()

```



Let's play with some colors. [Here are the color brewer choices](https://r-graph-gallery.com/38-rcolorbrewers-palettes.html)

Add scale_fill_brewer

```{r}
president |>
  ggplot(aes( x = party,fill=party) )+
  geom_bar()+
  scale_fill_brewer(palette = "Purples") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
           
```
Does color add anything to the graph above? 

Let's make a count plot of assortative mating. [Notice we are adding a shape aesthetic.](https://ggplot2.tidyverse.org/articles/ggplot2-specs.html) 

```{r}
assortative_mating |>
  ggplot(aes(x = self_male, y= partner_female, fill=self_male),)+
  geom_count(aes(color = partner_female), shape=23,stroke=1.5)  + 
  scale_fill_manual(values = c("blue","brown","green")) +
  scale_color_manual(values =  c("blue","brown","green")) +
  theme_bw()
```  

How do you feel about color in the above graph? 

Try this: 
- Make sure the above libraries are loaded.
- Take the cpr data set from the OpenIntro package
- Make a geom_bar() graph for the variable `group`
- Use the fill aesthetic to color the bars by outcome. 
- Add a scale_fill_brewer(palette= ) to play with different [brewer choices](https://r-graph-gallery.com/38-rcolorbrewers-palettes.html).


```{r}
cpr 
```
Copy most of the chunk you made above. 
- Try scale_fill_manual(values=c("","")) to manually set two colors for outcomes. 

Copy most of the chunck again and try scale_fill_fivethirtyeight()